---
title: "OSA Case - MLLB Report"
author: "Samy OUSSAIDENE"
date: "October, 29th"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

# EDA

```{r, echo=FALSE}
# Clear the working space
rm(list=ls())

Input_file <- "OSA_DB_UPM.xlsx"

Data_Directory <- "C:/Users/Samy/Desktop/OSA Case/"
```

```{r}
library(readxl)

df_OSA <- read_excel(paste(Data_Directory, Input_file, sep = ""))

df_OSA = as.data.frame(df_OSA)

df_OSA$Weight = as.numeric(df_OSA$Weight)  # need to convert character to numeric

library(dplyr)
df_OSA=filter(df_OSA,Weight>=0) ## remove NA

df_OSA$Gender=factor(df_OSA$Gender)

## Define of BMI
df_OSA$BMI <-
  with(df_OSA, Weight / (Height/100.0)^2)

## Add categorical feature OSA
#     Healthy (IAH <= 10)
#     Mild (10<IAH<30)
#     Severe (IAH >=30)

# We will use dplyr library (mutate operator)

df_OSA <- df_OSA %>%
          mutate(OSA = ifelse(IAH <= 10, "Healthy",
          ifelse(IAH>=30, "Severe", "Mild")))

```

# Categorical Features 

```{r}
barplot(table(df_OSA$Gender), col=c("steelblue4","steelblue1"))
```

```{r}
barplot(table(df_OSA$OSA), col=c("steelblue4","steelblue3","steelblue1"))
```

#Numerical Features

```{r}
## Describe the Database

df_OSA_bis=subset(df_OSA, select = -c(Gender,Patient,OSA))

summary(df_OSA_bis)

library(visdat)
vis_dat(df_OSA_bis)
```

```{r}
attach(df_OSA_bis)
layout(matrix(1:6,2,3))
hist(IAH,col="steelblue3")
hist(Weight,col="steelblue3")
hist(Height,col="steelblue3")
hist(BMI,col="steelblue3")
hist(Cervical,col="steelblue3")
hist(Age,col="steelblue3")
```

```{r}
attach(df_OSA_bis)
pairs(~ IAH + BMI + Weight + Height + Cervical + Age, col="steelblue3",
      main="Relations between variables")
```

```{r}
## PLOT Correlation Matrix

# FIRST
# install corrplot and then load it
library(corrplot)

#I noted that one patient didn't fill his Weight. So, it failed during the computation of correlation.
#So, I remove the corresponding row. But I could fill empty information by the mean of whole data. 
#library(dplyr)
#df_OSA_bis=filter(df_OSA_bis,Weight>=0) 

M <- cor(df_OSA_bis)  
corrplot(M, method="number")
corrplot(M, method="circle")
```

# Combine type of features

```{r}
attach(df_OSA)

df_OSA_male=subset(df_OSA, Gender=="hombre")
df_OSA_female=subset(df_OSA, Gender=="mujer")

df_OSA$OSA=factor(df_OSA$OSA)
df_OSA_healthy=subset(df_OSA, OSA=="Healthy")
df_OSA_mild=subset(df_OSA, OSA=="Mild")
df_OSA_severe=subset(df_OSA, OSA=="Severe")
```

```{r}
boxplot(df_OSA_male$IAH,df_OSA_female$IAH,col=c("steelblue4","steelblue1"))
title(main = "IAH depending on Gender")
legend("topright", c("Male", "Female"), fill=c("steelblue4","steelblue1"))
```

```{r}
boxplot(df_OSA_healthy$IAH,df_OSA_mild$IAH,df_OSA_severe$IAH,col=c("steelblue4","steelblue3","steelblue1"))
title(main = "IAH depending on OSA")
legend("topright", c("Healthy","Mild","Severe"), fill=c("steelblue4","steelblue3","steelblue1"))
```

```{r}
my_cols <- c("steelblue4", "steelblue1") 
pairs(~ IAH + BMI + Height + Weight + Cervical + Age, 
      col = my_cols[Gender],main="Relations between variables depending on Gender")
```

```{r}
my_cols <- c("steelblue4", "steelblue3","steelblue1") 
pairs(~ IAH + BMI + Height + Weight + Cervical + Age, 
      col = my_cols[df_OSA$OSA])
```

# Data Preparation

# Machine Learning Modelling

Linear Regression
```{r}
# Study the use of Simple and Multiple LR models
attach(df_OSA_bis)
lm.fit=lm(IAH~Weight+Height+Cervical+Age)

summary(lm.fit)
plot(lm.fit, col="steelblue2")
hist(lm.fit$residuals,col="steelblue2")
```

Study independently male and female populations
```{r}
### Male population
df_OSA_male=subset(df_OSA_bis, Gender==1)

# Another way
# df_OSA_male = df_OSA_C[df_OSA_C$Gender == 1, ]

names(df_OSA_male)
attach(df_OSA_male)

lm_male.fit=lm(IAH~Height+Cervical+Age+Weight)

summary(lm_male.fit)
hist(lm_male.fit$residuals,col="steelblue2")
```

```{r}
### Female population

df_OSA_female=subset(df_OSA_bis, Gender==2)
names(df_OSA_female)
attach(df_OSA_female)

lm_female.fit=lm(IAH~Height+Cervical+Age+Weight)

summary(lm_female.fit)
hist(lm_female.fit$residuals,col="steelblue2")
```

```{r}
attach(df_OSA_bis)

lm.fit=lm(IAH~BMI+Cervical+Age)

summary(lm.fit)
hist(lm.fit$residuals,col="steelblue2")
```


########################################
########################################
####   NEXT STEPS:
####
####  You can try:
####        - Regularization
####        - Feature selection
####        - other Regression models
####
####  BUT you can wait to see Classification Script
####           and use regression with some libraries as CARET
#### Comparison of Linear Regression with K Nearest Neighbors
  



