---
title: "R Notebook"
output: html_notebook
---

All SVM kernel methods are based on distance so it is required to scale variables prior to running final Support Vector Machine (SVM) model.

```{r}
rm(list=ls())
list=ls()
```

```{r, echo=FALSE}
library(dplyr)
library(readxl)
library(caret)
```

DATA IMPORTATION:
```{r}
Data_Directory <- "~/Desktop/OSA Case/Regression Notebook/"

setwd(Data_Directory)

train_file <- "train.xlsx"
test_file <- "test.xlsx"

train <- read_excel(paste(Data_Directory, train_file, sep = ""))
test <- read_excel(paste(Data_Directory, test_file, sep = ""))
```

LEARNING PROCESS:
I tried different c to find the best. each time, I reduce the interval. At the beginning, 1:5.Then 2:4:0.1. And finally,  
```{r}
set.seed(123)
train_Control <- trainControl(method="cv", number=10)
c <- expand.grid(C = seq(2,4,0.1)) 

SVM_linear <- train(IAH ~ Age+Cervical+BMI, data =train,
               method="svmLinear",trControl=train_Control, 
               preProcess= c("center","scale"), tuneGrid = c)

print(SVM_linear)
summary(SVM_linear)

print(SVM_linear$finalModel)
```

tuneLength to estimate a first tuning of hyperparameters: tuneLength = 3.

```{r}
set.seed(123)
train_Control <- trainControl(method="cv", number=10)

tune <- expand.grid(C = seq(0.1,0.3,0.05), scale = seq(0.5,1.5,0.25) , degree = 2) 

SVM_poly <- train(IAH ~ Age+Cervical+BMI, data = train,
               method="svmPoly",trControl=train_Control,
               preProcess= c("center","scale"), tuneGrid = tune)

print(SVM_poly)
summary(SVM_poly)

print(SVM_poly$finalModel)
```


```{r}
set.seed(123)
tune <- expand.grid(C = seq(0.25,0.75,0.1), sigma = seq(0.25,0.75,0.1)) 

SVM_radial <- train(IAH ~ Age+Cervical+BMI, data =train,
               method="svmRadial",trControl=train_Control, 
               preProcess= c("center","scale"), tuneGrid = tune)

print(SVM_radial)
summary(SVM_radial)

print(SVM_radial$finalModel)
```

```{r}
plot(SVM_linear)
plot(SVM_poly)
plot(SVM_radial)
```

PREDICTION PROCESS:
```{r}
pred_linear <- predict(SVM_linear,newdata=test)

pred_poly <- predict(SVM_poly,newdata=test)

pred_radial <- predict(SVM_radial,newdata=test)
```


```{r}
metrics1 = postResample(pred_linear, test$IAH)

metrics2 = postResample(pred_poly, test$IAH)

metrics3 = postResample(pred_radial, test$IAH)
```


```{r}
plot(abs(test$IAH-pred),xlab="IAH",type='p',col='blue')
```


```{r}
my_data = as.data.frame(cbind(predicted = pred_linear, observed = test$IAH))

# Plot predictions vs test data
ggplot(my_data,aes(predicted, observed)) + geom_point(color = "darkred", alpha = 0.5) + 
    geom_smooth(method=lm)+ ggtitle('Linear Regression ') + ggtitle("Linear regression: Prediction vs Test Data") +
      xlab("Predecited Power Output ") + ylab("Observed Power Output") + 
        theme(plot.title = element_text(color="darkgreen",size=16,hjust = 0.5),
         axis.text.y = element_text(size=12), axis.text.x = element_text(size=12,hjust=.5),
         axis.title.x = element_text(size=14), axis.title.y = element_text(size=14))
```

```{r}
my_data = as.data.frame(cbind(predicted = pred_poly, observed = test$IAH))

# Plot predictions vs test data
ggplot(my_data,aes(predicted, observed)) + geom_point(color = "darkred", alpha = 0.5) + 
    geom_smooth(method=lm)+ ggtitle('Linear Regression ') + ggtitle("Linear regression: Prediction vs Test Data") +
      xlab("Predecited Power Output ") + ylab("Observed Power Output") + 
        theme(plot.title = element_text(color="darkgreen",size=16,hjust = 0.5),
         axis.text.y = element_text(size=12), axis.text.x = element_text(size=12,hjust=.5),
         axis.title.x = element_text(size=14), axis.title.y = element_text(size=14))
```


```{r}
my_data = as.data.frame(cbind(predicted = pred_radial, observed = test$IAH))

# Plot predictions vs test data
ggplot(my_data,aes(predicted, observed)) + geom_point(color = "darkred", alpha = 0.5) + 
    geom_smooth(method=lm)+ ggtitle('Linear Regression ') + ggtitle("Linear regression: Prediction vs Test Data") +
      xlab("Predecited Power Output ") + ylab("Observed Power Output") + 
        theme(plot.title = element_text(color="darkgreen",size=16,hjust = 0.5),
         axis.text.y = element_text(size=12), axis.text.x = element_text(size=12,hjust=.5),
         axis.title.x = element_text(size=14), axis.title.y = element_text(size=14))
```


EXPORT OF DATA:
- import the excel file
```{r, setup, include=FALSE}
Data_Directory <- "~/Desktop/OSA Case/Results/"

knitr::opts_knit$set(root.dir = Data_Directory)

file <- "Regression Results.xlsx"

results <- read_excel(paste(Data_Directory, file, sep = ""))
```

- write into it and export:
```{r}
results$SVM_linear = metrics1

results$SVM_poly = metrics2

results$SVM_radial = metrics3

write_xlsx(results, paste(Data_Directory, file, sep = ""))
```
